Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-06-13 supplement.tex
Link to examples

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Usage with generative model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_error_violin_gen.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_1_full_pipeline}
  \caption{Example 1: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\input{example_1/esses.latex}
% has label tab:esses_example_1

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Usage with generative and candidate models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.7\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.5\textheight]{example_2/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.5\textheight]{example_2/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.45\textheight]{example_2/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_2/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.45\textheight]{example_2/true_posterior_best.png}
    };   
    \node[state] (DB) [right of = DG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_2/true_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_2_full_pipeline}
  \caption{Usage with generative and candidate models: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{example_2/esses_gen.latex}
% has label tab:esses_example_2_gen

\input{example_2/esses_best.latex}
% has label tab:esses_example_2_best

\input{example_2/evidence_true.latex}
% has label tab:evidences_example_2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Usage with generative and candidate models, compared to the background noise}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {1.0\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.5\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.4\textheight]{example_6/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.25\textheight]{example_6/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/true_posterior_best.png}
    };   
    \node[state] (DB) [below of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/true_error_violin_best.png}
    };   
    \node[state] (AT) [right of = A, rectangle, node distance=0.8\textheight] {
      \includegraphics[height=0.4\textheight]{example_6/twin_tree.png}
    };   
    \node[state] (BT) [below of = AT, rectangle] {
      \includegraphics[height=0.25\textheight]{example_6/twin_alignment.png}
    };   
    \node[state] (CTG) [right of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/twin_posterior_gen.png}
    };   
    \node[state] (DTG) [below of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/twin_error_violin_gen.png}
    };   
    \node[state] (CTB) [right of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/twin_posterior_best.png}
    };   
    \node[state] (DTB) [below of = CTB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/twin_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south east] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
      (A) edge [anchor = east] node {} (AT)
      (AT) edge [anchor = south] node {} (BT)
      (BT) edge [anchor = south east] node {} (CTG)
      (CTG) edge [anchor = south] node {} (DTG)
      (BT) edge [anchor = south] node {} (CTB)
      (CTB) edge [anchor = south] node {} (DTB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_3_full_pipeline}
  \caption{Usage with generative and candidate models, compared to the background noise: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{example_6/esses_gen.latex}
% has label tab:esses_example_3_gen

\input{example_6/esses_best.latex}
% has label tab:esses_example_3_best

\input{example_6/esses_twin_gen.latex}
% has label tab:esses_example_3_twin_gen

\input{example_6/esses_twin_best.latex}
% has label tab:esses_example_3_twin_best

\input{example_6/evidence_true.latex}
% has label tab:evidences_example_3

\input{example_6/evidence_twin.latex}
% has label tab:evidences_example_3

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Runtime}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}
  \begin{tabular}{ | r | c | }
    \hline
    \textbf{ERQ} & \textbf{run-time} \\ 
    \hline
      1 & 00:10:12 \\
      2 & 00:34:10 \\
      3 & 00:24:53 \\
      4 & 01:04:50 \\
      5 & 01:29:40 \\
    \hline
  \end{tabular}
  \caption{
    Time for an example research question to finish.
    Time is in in hh:mm::ss.
  }
  \label{tab:runtime}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Generative model only}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_1}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_error_violin_gen.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_1_full_pipeline}
  \caption{Generative model only: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\input{example_1/esses.latex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparing to other candidate models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_2}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.7\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.5\textheight]{example_2/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.5\textheight]{example_2/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.45\textheight]{example_2/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_2/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.45\textheight]{example_2/true_posterior_best.png}
    };   
    \node[state] (DB) [right of = DG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_2/true_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_2_full_pipeline}
  \caption{Comparing to other candidate models: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{example_2/esses_gen.latex}

\input{example_2/esses_best.latex}

\input{example_2/evidence_true.latex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparing to background noise}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_6}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {1.0\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.5\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.4\textheight]{example_6/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.25\textheight]{example_6/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/true_posterior_best.png}
    };   
    \node[state] (DB) [below of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/true_error_violin_best.png}
    };   
    \node[state] (AT) [right of = A, rectangle, node distance=0.8\textheight] {
      \includegraphics[height=0.4\textheight]{example_6/twin_tree.png}
    };   
    \node[state] (BT) [below of = AT, rectangle] {
      \includegraphics[height=0.25\textheight]{example_6/twin_alignment.png}
    };   
    \node[state] (CTG) [right of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/twin_posterior_gen.png}
    };   
    \node[state] (DTG) [below of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/twin_error_violin_gen.png}
    };   
    \node[state] (CTB) [right of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/twin_posterior_best.png}
    };   
    \node[state] (DTB) [below of = CTB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_6/twin_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south east] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
      (A) edge [anchor = east] node {} (AT)
      (AT) edge [anchor = south] node {} (BT)
      (BT) edge [anchor = south east] node {} (CTG)
      (CTG) edge [anchor = south] node {} (DTG)
      (BT) edge [anchor = south] node {} (CTB)
      (CTB) edge [anchor = south] node {} (DTB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_3_full_pipeline}
  \caption{Comparing to background noise: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{example_6/esses_gen.latex}

\input{example_6/esses_best.latex}

\input{example_6/esses_twin_gen.latex}

\input{example_6/esses_twin_best.latex}

\input{example_6/evidence_true.latex}

\input{example_6/evidence_twin.latex}
